\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/connor-mcshane/}{\Large Connor McShane - Senior Data Engineer}} & Email : \href{mailto:c.o.mcshane@gmail.com}{c.o.mcshane@gmail.com}\\
  \href{https://www.linkedin.com/in/connor-mcshane/}{https://www.linkedin.com/in/connor-mcshane/} & Mobile : +44-7494-211374 \\
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}
Seasoned Data Engineer with over 7 years of expertise across Cloud Landing Zones, Modern Data Stacks, Backend APIs, and Machine Learning solutions. Demonstrated success in both team leadership and individual contributor roles. Specialises in implementing comprehensive end-to-end data solutions, including batch and streaming data ingestion, infrastructure and application CI/CD, data modelling, and transforming raw data into actionable insights via dashboards and APIs. GCP-certified professional (7 certifications) with extensive cloud platform experience and a passion for cloud-based solutions.

%-----------SKILLS-----------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Technologies}{: Agentic Design, Terraform, GCP, GKE, SQL, DBT, PostgreSQL, Airflow, Apache Beam, PySpark, ML Pipelines, Python, Appscript, FastAPI, Airbyte, Gemini, Looker \& Looker Studio, Qlik, Google Analytics, Amplitude.}
    }
    \item{
      \textbf{Concepts}{: Cloud Architecture, Data Modelling, Data Warehousing, Streaming Pipelines, Serverless, DevOps, CI/CD, ML Pipelines, Vector Databases.}
    }
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------------
\section{Certifications}
  \resumeSubHeadingListStart
    \item{\small{Professional Machine Learning Engineer -- Google \textit{(May 2024)}}}
    \item{\small{Professional Cloud Security Engineer -- Google}}
    \item{\small{Professional Cloud Database Engineer -- Google \textit{(Sep 2023)}}}
    \item{\small{Professional Cloud Architect -- Google}}
    \item{\small{Professional Cloud Developer -- Google}}
    \item{\small{Professional Data Engineer -- Google}}
    \item{\small{Associate Cloud Engineer -- Google}}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Gumtree}{London, UK}
      {Senior Data Engineer}{Aug 2022 -- Present}
    \resumeItemListStart
      \resumeItem{Data Warehouse Migration}{Led migration of the data warehouse from Databricks on GCP to BigQuery, improving performance and reducing operational complexity.}
      \resumeItem{GCP Data Architecture}{Served as principal architect for GCP data projects, designing IAM policies and end-to-end ingestion, transformation, and presentation layers.}
      \resumeItem{DBT Stack Implementation}{Built and deployed the full DBT stack including Airflow on Cloud Composer, with Terraform-managed infrastructure and CI/CD pipelines. Integrated Elementary for custom data anomaly detection and freshness alerting.}
      \resumeItem{Data Governance}{Designed and implemented a data governance architecture using GCP policy tags and column-level security. Built a custom service applying regex-based policy tag propagation across datasets, and deployed Cloud DLP PII scanning with automated alerting.}
      \resumeItem{Open Source Airbyte Deployment}{Deployed and managed a self-hosted Airbyte instance on GKE using Terraform for scalable, cost-effective data ingestion.}
      \resumeItem{Autocomplete Search Pipeline}{Architected and delivered a backend autocomplete search pipeline driven by user search history data.}
      \resumeItem{User Data Deletion Tool}{Developed an in-house user data deletion tool, replacing a third-party solution and saving Gumtree \pounds100K annually.}
      \resumeItem{BigQuery Cost Optimisation}{Designed a BigQuery slot reservation architecture saving \pounds120K annually.}
      \resumeItem{Team Development}{Mentored junior engineers and supported analysts, delivering training on BigQuery, Looker Studio, and DBT.}
    \resumeItemListEnd

    \resumeSubheading
      {Lab151 Technologies}{Remote}
      {Founder \& Lead Data Engineer (Consulting)}{Mar 2021 -- Aug 2022}
    \resumeItemListStart
      \resumeItem{Napster -- AI Search}{Implemented an AI-powered search backend service processing user queries with Gemini to fetch results from a Mongo-based Content Management System.}
      \resumeItem{Napster -- Algorithmic Playlists}{Built all recommendation APIs and algorithmic playlists, leveraging usage data and content embeddings to enhance personalisation and user engagement.}
      \resumeItem{Napster -- Cost Optimisation}{Developed models and dashboards for GCP budget spend and BigQuery job monitoring, identifying inefficiencies and optimising query execution to save over \$400K annually.}
      \resumeItem{Napster -- Data Governance}{Designed and implemented a PII masking tool using Cloud DLP to scan tables and apply appropriate tags to mask sensitive data on the fly.}
      \resumeItem{Napster -- API Migration}{Led the migration of 8 backend services from on-prem to Cloud Run serverless, including database migrations from on-prem Cassandra to Firestore.}
      \resumeItem{Napster -- Dashboarding}{Built interactive dashboards in Qlik and Looker Studio and created an internal report bursting tool for 300 partner reports, saving \$80K annually in SaaS costs.}
      % Add 66 Degrees bullets here when ready
    \resumeItemListEnd

    \resumeSubheading
      {Dojo}{London, UK}
      {Senior Data Engineer}{Mar 2021 -- May 2022}
        \resumeItemListStart
         \resumeItem{Near Real-Time Customer Engagement}{Connected Braze with customer data models enabling near real-time state changes to drive personalised engagement in the Dojo app.}
          \resumeItem{Embedded Analytics}{Deployed a Looker Embed internal API, enabling internal applications to display Looker dashboards with dynamic data visualisations.}
          \resumeItem{BigQuery Cost Optimisation}{Implemented BigQuery Flexi slot allocation strategy, reducing query costs by 30--40\%, leading to annual savings of \$300K.}
          \resumeItem{Custom Data Pipelines}{Developed bespoke ingestion pipelines to streamline data movement and transformation across the organisation.}
          \resumeItem{Data Mesh Tooling}{Implemented Python packages to support Data Mesh architecture within Dojo.}
        \resumeItemListEnd

    \resumeSubheading
      {Jellyfish}{London, UK}
      {Data Engineer}{Mar 2020 -- Mar 2021}
        \resumeItemListStart
          \resumeItem{SEO Analytics Products}{Led the development of Share of Demand and JIQ products, providing SEO insights to clients and enabling them to optimise marketing strategies.}
          \resumeItem{Data Pipeline Development}{Designed and implemented Airflow data pipelines for multiple clients, improving data ingestion and processing efficiency.}
          \resumeItem{Standardised Delivery Framework}{Created a standardised delivery model for Data Engineering projects in GCP from discovery to implementation, helping Jellyfish achieve GCP Data Analytics Specialization and open new revenue streams.}
        \resumeItemListEnd

    \resumeSubheading
      {GFT Group}{London, UK}
      {Cloud Engineer}{Sep 2019 -- Mar 2020}
        \resumeItemListStart
          \resumeItem{Cloud Landing Zone}{Developer on Tranquillity Base, a GCP landing zone solution using Packer and Terraform enabling one-click deployment for cloud environments.}
          \resumeItem{BigQuery Ingestion CI/CD}{Designed and implemented CI/CD pipelines for a BigQuery ingestion tool at HSBC, allowing internal business functions to create and manage data stacks with repeatability and efficiency.}
          \resumeItem{Infrastructure Automation}{Created Jenkins pipelines to automate testing and deployment of infrastructure, improving reliability and reducing manual intervention.}
        \resumeItemListEnd

    \resumeSubheading
      {PA Consulting Group}{London, UK}
      {Analyst Consultant}{Apr 2018 -- Sep 2019}
        \resumeItemListStart
          \resumeItem{IoT Platform Development}{Lead GCP developer on a streaming IoT platform for a FTSE250 pest control company, creating Apache Beam pipelines to process data and provide real-time alerts.}
          \resumeItem{API Development}{Developed REST APIs to access stored data across Cloud Spanner, Datastore, and BigQuery.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The University of Western Australia}{Perth, Australia}
      {Master of Electrical Engineering, High Distinction (First Class equivalent)}{Jan 2015 -- Dec 2017}
    \resumeSubheading
      {Technical University of Denmark (DTU)}{Denmark}
      {Master's Exchange, Electrical and Electronics Engineering}{Jan 2017 -- Jun 2017}
    \resumeSubheading
      {The University of Western Australia}{Perth, Australia}
      {Bachelor of Science (Software Engineering), High Distinction (First Class equivalent)}{Jan 2012 -- Dec 2014}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}